NumPy---Array Computation for Python

### 2019-12-18 paper.tex
BUG: Fix grammar
Fix error
ENH: Wrap classes in code
Wrap classes in code decoration

The NumPy random module provides pseudorandom numbers from a wide range of
distributions. In legacy versions of NumPy, simulated random values are produced
by a RandomState object that: handles seeding and state initialization; wraps
the core pseudorandom number generator based on a 32-bit implementation of
MT19937; interfaces with the underlying code that transforms random bits into
deviates from other distributions; and supplies a singleton instance exposed in
the root of the random module.

The RandomState object makes a compatibility guarantee so that a fixed seed and
sequence of function calls produce the same set of values. This guarantee has
slowed progress since improving the underlying code requires extending the API
with additional keyword arguments. This guarantee continues to apply to
RandomState.

NumPy 1.17 introduced a new API for generating random numbers that use a more
flexible structure that can be extended by libraries or end-users. The new API
is build using components separate the tasks needed when generating random
variates. Pseudorandom bits are generated by a bit generator. These bits are
then transformed into variates from complex distributions by a generator.
Finally, seeding is handled by an object that produces sequences of high-quality
initial values.

@@

The Generator consumes one of the bit generators and produces variates from
complicated distributions. Many improved methods for generating random variates
from common distributions were implemented, including the Ziggurat method for
normal, exponential and gamma variates\cite{ziggurat}, and Lemire's method for
bounded random integer generation\cite{lemire}. The Generator is more similar to
the legacy RandomState, and its API is substantially the same. The key
differences all relate to state management, which has been delegated to the bit
generator. The Generator does not make the same stream guarantee as the
RandomState object, and so variates may differ across versions as improved
generation algorithms are introduced.\footnote{Despite the removal of the
compatibility guarantee, simple reproducibility across versions is encouraged,
and minor changes that do not produce meaningful performance gains or fix
underlying bug are not generally adopted.}

Finally, a SeedSequence is used to initialize a bit generator. The seed sequence
can be initialized with no arguments, in which case it reads entropy from a
system-dependent provider, or with a user-provided seed. The seed sequence then
transforms the initial set of entropy into a sequence of high-quality
pseudorandom integers, which can be used to initialize multiple bit generators
deterministically. A key design goal of a seed sequence was to be splittable in
the sense that a seed sequence can be used to produce child sequences that are
distinct from their parents or other ancestors. This capability allows a seed
sequence to be used in large distributed applications where the number of
workers required is not known. The sequences generated from the same initial
entropy and the same splits are fully deterministic to ensure reproducibility.

@@

\noindent While this approach retains complete flexibility, the method
\code{np.random.default\_rng} can be used to instantize a Generator when
reproducibility is not needed.

The final goal of the new API is to improve extensibility. RandomState is a
monolithic object that obscures all of the underlying state and functions. The
component architecture is one part of the extensibility improvements. The
underlying functions (written in C) which transform the output of a bit
generator to other distributions are available for use in CFFI. This allows the
same code to be run in both NumPy and dependent that can consume CFFI, e.g.,
numba. Both the bit generators and the low-level functions can also be used in C
or Cython code.\footnote{As of 1.18.0, this scenario requires access to the
NumPy source. Alternative approaches that avoid this extra step are being
explored.}

>>>>

The NumPy random module provides pseudorandom numbers from a wide range of
distributions. In legacy versions of NumPy, simulated random values are produced
by a \code{RandomState} object that: handles seeding and state initialization; wraps
the core pseudorandom number generator based on a 32-bit implementation of
MT19937; interfaces with the underlying code that transforms random bits into
deviates from other distributions; and supplies a singleton instance exposed in
the root of the random module.

The \code{RandomState} object makes a compatibility guarantee so that a fixed seed and
sequence of function calls produce the same set of values. This guarantee has
slowed progress since improving the underlying code requires extending the API
with additional keyword arguments. This guarantee continues to apply to
\code{RandomState}.

NumPy 1.17 introduced a new API for generating random numbers that use a more
flexible structure that can be extended by libraries or end-users. The new API
is built using components that separate the steps required to generate random
variates. Pseudorandom bits are generated by a bit generator. These bits are
then transformed into variates from complex distributions by a generator.
Finally, seeding is handled by an object that produces sequences of high-quality
initial values.

@@

The \code{Generator} consumes one of the bit generators and produces variates from
complicated distributions. Many improved methods for generating random variates
from common distributions were implemented, including the Ziggurat method for
normal, exponential and gamma variates\cite{ziggurat}, and Lemire's method for
bounded random integer generation\cite{lemire}. The \code{Generator} is more similar to
the legacy \code{RandomState}, and its API is substantially the same. The key
differences all relate to state management, which has been delegated to the bit
generator. The \code{Generator} does not make the same stream guarantee as the
\code{RandomState} object, and so variates may differ across versions as improved
generation algorithms are introduced.\footnote{Despite the removal of the
compatibility guarantee, simple reproducibility across versions is encouraged,
and minor changes that do not produce meaningful performance gains or fix
underlying bug are not generally adopted.}

Finally, a \code{SeedSequence} is used to initialize a bit generator. The seed sequence
can be initialized with no arguments, in which case it reads entropy from a
system-dependent provider, or with a user-provided seed. The seed sequence then
transforms the initial set of entropy into a sequence of high-quality
pseudorandom integers, which can be used to initialize multiple bit generators
deterministically. A key design goal of a seed sequence was to be splittable in
the sense that a seed sequence can be used to produce child sequences that are
distinct from their parents or other ancestors. This capability allows a seed
sequence to be used in large distributed applications where the number of
workers required is not known. The sequences generated from the same initial
entropy and the same splits are fully deterministic to ensure reproducibility.

@@

\noindent While this approach retains complete flexibility, the method
\code{np.random.default\_rng} can be used to instantize a \code{Generator} when
reproducibility is not needed.

The final goal of the new API is to improve extensibility. \code{RandomState} is a
monolithic object that obscures all of the underlying state and functions. The
component architecture is one part of the extensibility improvements. The
underlying functions (written in C) which transform the output of a bit
generator to other distributions are available for use in CFFI. This allows the
same code to be run in both NumPy and dependent that can consume CFFI, e.g.,
numba. Both the bit generators and the low-level functions can also be used in C
or Cython code.\footnote{As of 1.18.0, this scenario requires access to the
NumPy source. Alternative approaches that avoid this extra step are being
explored.}
